The SMT Competition 2015--2018

### 2019-08-30 2018/report/table-winners-main-24s.tex
Report: Tweak winners table layout.

\begin{table}
  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds.}
  \label{tab:results:24s}
  \centering

  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division   &  2015             &  2016                      &  2017                     &  2018                                  \\
    \hline \hline
    AUFLIA     &                   & \cc{vamp} Vampire \nc{Z3}  & \cc{verit} veriT          &                                        \\
    AUFLIRA    & \cc{cvc3} CVC3    &                            &                           & -/Alt-Ergo                             \\
    AUFNIRA    & \nonc \nc{Z3}     &                            &                           & \nc{Z3}                                \\
    BV         &                   &                            &                           & \cc{bool} Boolector/Boolector \nc{Z3}  \\
    NRA        &                   &                            &                           & \cc{cvc4} CVC4/CVC4 \nc{Z3}            \\
    QF\_ABV    &                   & \cc{yices} Yices2          &                           &                                        \\
    QF\_ANIA   &                   & \nonc \nc{Z3}              & \nonc \nc{Z3}             &                                        \\
    QF\_BV     & \cc{cvc4} CVC4    & \cc{stp} STP \nc{Z3}       &                           & -/Boolector                            \\
    QF\_LIA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         &                                        \\
    QF\_LRA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
    QF\_NIA    &                   &                            & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
    QF\_NIRA   &                   &                            & \cc{yices} Yices2 \nc{Z3} & \cc{yices} Yices2 \nc{Z3}              \\
    QF\_NRA    &                   &                            & \nc{Z3}                   &                                        \\
    QF\_UF     & \cc{verit} veriT  & \cc{verit} veriT           &                           &                                        \\
    QF\_UFNRA  &                   & \cc{cvc4} CVC4 \nc{Z3}     & \cc{cvc4} CVC4            & \nc{Z3}                                \\
    UF         &                   & \cc{vamp} Vampire          &                           &  \cc{vamp} Vampire/-                   \\
    UFBV       &                   & \cc{bool} Boolector        &                           &                                        \\
    UFIDL      &                   & \cc{vamp} Vampire \nc{Z3}  & \nc{Z3}                   &                                        \\
    UFLIA      &                   &                            &                           & \nc{Z3}                                \\
    UFLRA      &                   &                            & \cc{verit} veriT          & \cc{verit} veriT                       \\
    UFNIA      & \nonc \nc{Z3}     &                            &                           & \cc{cvc4} CVC4/\nc{Z3}                 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds. NEW}

@@

  \scalebox{.82}{%

>>>>

@@

  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds.}

@@

  \scalebox{.755}{%

### 2019-08-30 2018/report/table-winners-main-families.tex
Report: Tweak winners table layout.

\begin{table}
  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used)}
  \label{tab:results:total:solved}
  \centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division & 2015 &  2016           &  2017                &  2018                  \\
    \hline\hline
    AUFNIRA  &      & \cc{cvc4} CVC4  &                      &                        \\
    UFIDL    &      & \nc{Z3}         &                      &                        \\
    BV       &      &                 & \cc{bool} Boolector  &                        \\
    QF\_LRA  &      &                 & \cc{yices} Yices2    & \cc{spass} SPASS-SATT  \\
    QF\_NIA  &      &                 & \cc{yices} Yices2    & \cc{yices} Yices2      \\
    QF\_BV   &      &                 &                      & -/Boolector            \\
    QF\_FP   &      &                 &                      & \cc{cvc4} CVC4         \\
  \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used). NEW}
  \label{tab:results:total:solved}
  \centering
  {%
    \renewcommand{\arraystretch}{1.01}%

>>>>

\begin{table}
  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
  \label{tab:results:total:solved}
  \centering
  \scalebox{.755}{%
    \renewcommand{\arraystretch}{1.01}%

### 2019-08-30 2018/report/table-winners-main-sat-unsat.tex
Report: Tweak winners table layout.

\begin{table}
  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:sat}
\centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division         &  2015                &  2016                   &  2017                   &  2018                     \\
    \hline \hline
    ALIA             &                      &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIA           & \cc{cvc3} CVC3       &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIRA          &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{alt} Alt-Ergo         \\
    AUFNIRA          & \nonc\nc{Z3}         & \cc{cvc4} CVC4 \nc{Z3}  & \cc{cvc4} CVC4 \nc{Z3}  & \nc{Z3}                   \\
    BV               &                      & \nc{Z3}                 & \cc{bool} Boolector     & \cc{bool} Boolector       \\
    LRA              &                      &                         & \cc{verit} veriT        &                           \\
    NIA              & \nonc \cc{cvc3} CVC3 &                         &                         &                           \\
    NRA              & \nonc \cc{cvc3} CVC3 & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4 \nc{Z3}    \\
    QF\_ABV          &                      & \cc{yices} Yices2       & \cc{yices} Yices2       &                           \\
    QF\_AUFBV        & \cc{yices} Yices     & \cc{yices} Yices2       &                         & \cc{yices} Yices2         \\
    QF\_BV           &                      & \nc{Z3}/MinkeyRink      &                         &                           \\
    QF\_FP           &                      &                         &                         & \cc{cvc4} CVC4            \\
    QF\_LIA          & \nc{Z3}              &                         &                         &                           \\
    QF\_LRA          &                      &                         & \cc{yices} Yices2       & \cc{yices} Yices2         \\
    QF\_NIA          &                      & \cc{rat} SMT-RAT        &                         &                           \\
    QF\_NIRA         &                      &                         & \cc{cvc4} CVC4          &                           \\
    QF\_NRA          &                      &                         & \nc{Z3}                 &                           \\
    QF\_UFBV         &                      &                         &                         & \cc{yices} Yices2         \\
    QF\_UFIDL        & \nc{Z3}              & \nc{Z3}                 & \nc{Z3}                 & \cc{verit} veriT  \nc{Z3} \\
    QF\_UFNIA        & \nonc \cc{cvc3} CVC3 &                         & \cc{cvc4} CVC4          &                           \\
    UF               &                      & \cc{vamp} Vampire       &                         & \cc{vamp}Vampire/-        \\
    UFBV             &                      & \cc{bool} Boolector     &                         &                           \\
    UFDTLIA          &                      &                         & \nonc \cc{cvc4} CVC4    &                           \\
    UFLIA            & \nc{Z3}              &                         &                         &                           \\
    UFLRA            &                      & \cc{cvc4} CVC4          &                         &                           \\
    UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\
    \bottomrule
  \end{tabular}
\end{table}

@@

  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}

@@

  \scalebox{.82}{%

@@

\begin{table}
  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:unsat}
  \centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
\toprule
Division        &  2015                  &  2016                     &  2017                 &  2018                   \\
\hline \hline
    BV          &                        & \cc{cvc4} CVC4            &                       &                         \\
    NIA         &                        & \cc{cvc4} CVC4            & \cc{vamp} Vampire     & \cc{vamp} Vampire       \\
    QF\_AUFBV   &                        &                           & \cc{cvc4} CVC4        &                         \\
    QF\_AUFNIA  & \nonc \nc{Z3}          & \nonc \nc{Z3}             &                       &                         \\
    QF\_BV      &                        &                           & -/Boolector           &                         \\
    QF\_IDL     & \cc{cvc4} CVC4         &                           & \nc{Z3}               & \cc{cvc4} CVC4 \nc{Z3}  \\
    QF\_LIA     & \cc{smti} SMTInterpol  & \cc{smti} SMTInterpol     & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol   \\
    QF\_NIA     & \cc{cvc3} CVC3         &                           & \cc{yices} Yices2     &                         \\
    QF\_NRA     &                        &                           &                       & \cc{cvc4} CVC4          \\
    QF\_UFLIA   &                        &                           & \nc{Z3}               &                         \\
    QF\_UFNRA   &                        & \cc{cvc4} CVC4 \nc{Z3}    & \cc{cvc4} CVC4        & \cc{cvc4} CVC4 \nc{Z3}  \\
    UF          &                        &                           & \cc{cvc4} CVC4        & -/CVC4                  \\
    UFIDL       &                        & \cc{vamp} Vampire \nc{Z3} & \nc{Z3}               &                         \\
    UFLRA       &                        &                           & \cc{verit} veriT      & \cc{verit} veriT        \\
    \bottomrule
  \end{tabular}

@@

  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}

@@

\begin{tabular}{r>{\columncolor{white}[.25em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][0.5em]}c}

>>>>

@@

  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}

@@

  \scalebox{.747}{%

@@

@@

  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}

@@

### 2019-08-30 2018/report/table-winners-main-unknown.tex
Report: Tweak winners table layout.

\begin{table}
  \caption{Alternative best solvers if benchmarks with unknown status had not bee included in 2017 onwards.}
  \label{tab:results:unknowns}
  \centering
    \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division &  2017          &  2018                  \\
    \hline\hline
    AUFNIRA  & \cc{cvc4} CVC4 &                        \\
    QF\_NIRA & \nc{Z3}        & \cc{cvc4} CVC4 \nc{Z3} \\
    QF\_NRA  & \nc{Z3}        &                        \\
    UFDTLIA  & \cc{cvc4} CVC4 &                        \\
    BV       &                & \cc{bool} Boolector    \\
    QF\_FP   &                & \cc{cvc4} CVC4 \nc{Z3} \\
    UFNIA    &                & \cc{cvc4} CVC4         \\
    NRA      &                & -/\nc{Z3}              \\
    UF       &                & -/CVC4                 \\
  \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not bee included in 2017 onwards.}
  \label{tab:results:unknowns}
  \centering
  \scalebox{.755}{%
    \renewcommand{\arraystretch}{1.01}%
\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
\toprule
Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
\midrule
AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                                 \cc{cvc4} CVC4 [Z3] &  \hspace*{3em}         &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
LRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
NRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                   & \cc{vamp} Vampire [Z3] \\
QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
UF       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                            \cc{cvc4} CVC4 &  &                                                           & \cc{cvc4} CVC4 \\
UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     \cc{cvc4} CVC4 [Z3] &  \\
\bottomrule
\end{tabular}
  }
\end{table}

### 2019-08-30 2018/report/table-winners-main.tex
Report: Tweak winners table layout.

\begin{table}
\caption{Best \maintrack solvers (by division)}
\label{tab:winners-main}
\centering
\scalebox{.82}{%
\renewcommand{\arraystretch}{1.01}%
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    Division         &  2015                        &  2016                     &  2017                           &  2018                     \\
    \wc ABVFP        &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
    \rc{cvc4}
    \wc ALIA         & CVC4 \nc{Z3}                 & CVC4 \nc{Z3}              & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
    \wc AUFBVDTLIA   &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
    \wc AUFDTLIA     &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
    \rc{cvc4}
    \wc AUFLIA       & {CVC4}                       & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
    \rc{vamp}
    \wc AUFLIRA      & \cc{cvc4} CVC4 \nc{Z3}       & Vampire \nc{Z3}           & Vampire \nc{Z3}                 & \cc{cvc4} CVC4 \nc{Z3}    \\
    \rc{vamp}
    \wc AUFNIRA      & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & \cc{cvc4} {CVC4}          \\
    \rc{q3b}
    \wc BV           & \nonc \cc{cvc4} CVC4 \nc{Z3} & {Q3B}                     & Q3B \nc{Z3}                     & \cc{cvc4} {CVC4}          \\
    \wc BVFP         &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
    \wc FP           &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
    \rc{cvc4}
    \wc LIA          & {CVC4}                       & {CVC4}                    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
    \rc{cvc4}
    \wc LRA          & {CVC4}                       & {CVC4}                    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
    \rc{cvc4}
    \wc NIA          & \nonc CVC4 \nc{Z3}           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
    \rc{vamp}
    \wc NRA          & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & \cc{redl} {Redlog}              & Vampire \nc{Z3} / Vampire \\
    \rc{bool}
    \wc QF\_ABV      & {Boolector}                  & {Boolector}               & {Boolector}                     & {Boolector}               \\
    \wc QF\_ABVFP    &                              &                           & {---}                           & \cc{cvc4} {CVC4}          \\
    \rc{yices}
    \wc QF\_ALIA     & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{cvc4}
    \wc QF\_ANIA     & \nonc CVC4 \nc{Z3}           & \nonc {CVC4}                & \nonc {CVC4}                  & \nonc CVC4 \nc{Z3}        \\
    \rc{cvc4}
    \wc QF\_AUFBV    & CVC4 \nc{MathSAT}            & CVC4 \nc{MathSAT}         & \cc{yices} Yices2 \nc{MathSAT}  & {CVC4}                    \\
    \rc{yices}
    \wc QF\_AUFLIA   & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{cvc4}
    \wc QF\_AUFNIA   & \nonc {CVC4}                 & \nonc {CVC4}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
    \rc{yices}
    \wc QF\_AX       & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{bool}
    \wc QF\_BV       & {Boolector}                  & {Boolector}               & {Boolector/MinkeyRink}          & {Boolector/MinkeyRink}    \\
    \wc QF\_BVFP     & \nonc \cc{z} {Z3}            & \nonc \wc \nc{Z3}         & \nonc \cc{coli} COLIBRI \nc{Z3} & \cc{cvc4} {CVC4}          \\
    \wc QF\_DT       &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
    \rc{coli}
    \wc QF\_FP       & \nonc \cc{z} {Z3}            & \nonc \wc \nc{MathSAT}    & COLIBRI \nc{Z3}                 & {COLIBRI}                 \\
    \rc{yices}
    \wc QF\_IDL      & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & {Yices2}                  \\
    \rc{cvc4}
    \wc QF\_LIA      & CVC4 \nc{MathSAT}            & CVC4 \nc{MathSAT}         & CVC4 \nc{MathSAT}               & \cc{spass} {SPASS-SATT}   \\
    \rc{yices}
    \wc QF\_LIRA     & {Yices2}                     & {Yices2}                  & Yices2 \nc{Z3}                  & Yices2 \nc{Z3}            \\
    \rc{cvc4}
    \wc QF\_LRA      &  {CVC4}                      & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
    \rc{cvc4}
    \wc QF\_NIA      & \cc{apr} AProVE \nc{Z3}      & \cc{yices} Yices2 \nc{Z3} & {CVC4}                          & {CVC4}                    \\
    \rc{cvc4}
    \wc QF\_NIRA     & {CVC4}                       & {CVC4}                    & \cc{rat} {SMT-RAT}              & \cc{rat} {SMT-RAT}        \\
    \rc{yices}
    \wc QF\_NRA      & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & Yices2 \nc{Z3}            \\
    \rc{yices}
    \wc QF\_RDL      & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \wc QF\_SLIA     &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
    \rc{yices}
    \wc QF\_UF       & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{bool}
    \wc QF\_UFBV     & {Boolector}                  & {Boolector}               & {Boolector}                     & {Boolector}               \\
    \rc{yices}
    \wc QF\_UFIDL    & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{yices}
    \wc QF\_UFLIA    & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & {Yices2}                  \\
    \rc{yices}
    \wc QF\_UFLRA    & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
    \rc{yices}
    \wc QF\_UFNIA    & \nonc \cc{cvc4} {CVC4}       & {Yices2/CVC4}             & {Yices2}                        & {Yices2}                  \\
    \rc{yices}
    \wc QF\_UFNRA    & \nonc \cc{cvc3} CVC3 \nc{Z3} & {Yices2}                  & Yices2 \nc{Z3}                  & {Yices2}                  \\
    \rc{cvc4}
    \wc UF           & {CVC4}                       & {CVC4}                    & \cc{vamp} {Vampire}             &  {CVC4/Vampire}           \\
    \rc{cvc4}
    \wc UFBV         & \nonc CVC4 \nc{Z3}           & CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
    \wc UFDT         &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
    \wc UFDTLIA      &                              &                           & \nonc \cc{vamp} {Vampire}       & \cc{cvc4} {CVC4}          \\
    \rc{cvc4}
    \wc UFIDL        & CVC4 \nc{Z3}                 & {CVC4}                    & {CVC4}                          & CVC4 \nc{Z3}              \\
    \rc{cvc4}
    \wc UFLIA        & {CVC4}                       & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
    \rc{cvc4}
    \wc UFLRA        & \cc{cvc3} {CVC3}             & \cc{vamp} Vampire \nc{Z3} & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
    \rc{vamp}
    \wc UFNIA        & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & Vampire \nc{Z3} / Vampire \\
  \end{tabular}}

\begin{table}
\caption{Best \maintrack solvers (by division). NEW}
\label{tab:winners-main}
\centering
\scalebox{.82}{%
\renewcommand{\arraystretch}{1.01}%

>>>>

\begin{table}
\caption{Best \maintrack solvers (by division).}
\label{tab:winners-main}
\centering
\scalebox{.755}{%
\renewcommand{\arraystretch}{1.01}%
